Effects of the body force on the evacuation dynamics

### 2019-12-31 paper.tex
complete un poco el texto de network en bottleneck

>>>>

The four configurations corresponds to two different $v_d$ and two different $k$ values. Fig. \ref{network_vd2_kn0} represents $v_d=$2 and $k=0$, Fig. \ref{network_vd10_kn0} corresponds to $v_d=$10 and $k=0$ while \ref{network_vd2_kn1200000} and \ref{network_vd10_kn1200000} correspond to $v_d=$2 and $v_d=$10 respectively and both have the same body force coefficient $k=$1.2~E6. As expected, increasing the desired velocity compress the crowd towards the exit. \\

Comparing Fig. \ref{network_vd2_kn0} against Fig. \ref{network_vd2_kn1200000} and Fig \ref{network_vd10_kn0} against Fig. \ref{network_vd10_kn1200000} it is clear that increasing the stiffness reduces the degree. The most notorious case is the pictures corresponding to $v_d=$10 in which, despite having the same $v_d$, the size of the bulk increases when the pedestrians are stiffer. Moreover, when pedestrians are stiffer they have fewer contacts in general (less degree). Notice that there are no pedestrians with degree 6 when $k=1.2$~E6 and there are a lot of pedestrians with degree 6 when $k$=0.
